---
title: "Main documentation"
author: "Thibaut Koutangni"
date: "October 2016"
output: 
    html_document:
        fig.width: 10
        fig.height: 8
---

This document present outputs of my models simulations.
It allow reproducing the results of my modelling work.
I'm happy to clarify and discuss any question you have with regard to the output.
my email: <koutibaut@yahoo.fr> if needed.


**Notice!! : **
The file `run_first.R` in the R/ folder contains, functions, packages, and script needed to reproduce the analysis and must be sourced first. (see code chunck named: `sourcefirst`)

```{r setup, cache=FALSE, include=FALSE}
library(knitr)
output <- opts_knit$get("rmarkdown.pandoc.to")
if (output=="html") opts_chunk$set(fig.width=10, fig.height=8, message=FALSE, warning=FALSE, results="asis", cache = TRUE)
#if (output=="docx") opts_chunk$set(fig.width=6,  fig.height=6)
```


```{r sourcefirst, include=TRUE, cache=FALSE, message=FALSE, results="hide"}
# source the script that load, the packages, functions, and data needed for 
# the analysis
source('R/run_first.R')
```

### Sample simulations of the SCIRS Model

#### 1. Simulating the model with no forcing and no age structure

```{r echo=TRUE}

# simulate model
sim1 = sample_sim(epsilon_a = 0.0, epsilon_b = 0.0, forcing_invasion = FALSE, nyears = 5, age_structured = FALSE)
# subset model output and choose variables to plot.
melt_sim1 =  melt_any_data.frame(sim1, "time", c("Susc", "Carrier", "Recov"))
melt_sim1_cases = melt_any_data.frame(sim1, "time", c("newI", "Ill"))

```

```{r echo=FALSE, fig.width=11, fig.height=4, fig.align='center'}

# Plot simulations
# Plot selected variables except cases
p1<-ggplot_sim_output(sim_output_melt = melt_sim1, time_step = year, tick_label_evry = 1)
# plot cases (iIncidence (NewI), and prevalence (Ill)) separetely with prevalence of cases
p2<-ggplot_sim_output(sim_output_melt = melt_sim1_cases, time_step = year, tick_label_evry = 1)
# output the plots p1 and p2 in a two column display
multi_ggplot(p1,p2 ,cols = 2)
#plotAllModelVariables(sim1)
```

```{r echo=FALSE}
# leave this intentionaly blank
```
+ ##### Figure caption: Plot of model simulation with no forcing and no age structure.


#### 2. Simulating the model with no age structure by imposing seasonal forcing on the risk of disease among colonized individuals (i.e., the invasion rate)
```{r echo=TRUE}

sim2 = sample_sim(epsilon_a = 0.1, epsilon_b = 0.0, forcing_invasion = TRUE, nyears = 5, age_structured = FALSE)
# subset model output and choose variables to plot.
melt_sim2 =  melt_any_data.frame(sim2, "time", c("Susc", "Carrier", "Recov"))
melt_sim2_cases = melt_any_data.frame(sim2, "time", c("newI", "Ill"))

```

```{r echo=FALSE, fig.width=11, fig.height=4, fig.align='center'}

# Plot simulations
# Plot selected variables except cases
p3<-ggplot_sim_output(sim_output_melt = melt_sim2, time_step = year, tick_label_evry = 1)
# plot cases (iIncidence (NewI), and prevalence (Ill)) separetely with prevalence of cases
p4<-ggplot_sim_output(sim_output_melt = melt_sim2_cases, time_step = year, tick_label_evry = 1)
# output the plots p1 and p2 in a two column display
multi_ggplot(p3,p4 ,cols = 2)

```

```{r echo=FALSE}
# leave intentionally blank for formating purpose
```

+ ##### Figure caption: Plot of model simulation with no age structure but seasonal forcing of invasion parameter alone.

#### 3. Simulating the model with no age structure by imposing seasonal forcing on the transmission of the bacteria
```{r echo=TRUE}
sim3 = sample_sim(epsilon_a = 0.0, epsilon_b = 0.1, forcing_invasion = FALSE, nyears = 5, age_structured = FALSE)
# subset model output and choose variables to plot.
melt_sim3 =  melt_any_data.frame(sim3, "time", c("Susc", "Carrier", "Recov"))
melt_sim3_cases = melt_any_data.frame(sim3, "time", c("newI", "Ill"))

```

```{r echo=FALSE, fig.width=11, fig.height=4, fig.align='center'}

# Plot simulations
# Plot selected variables except cases
p5<-ggplot_sim_output(sim_output_melt = melt_sim3, time_step = year, tick_label_evry = 1)
# plot cases (iIncidence (NewI), and prevalence (Ill)) separetely with prevalence of cases
p6<-ggplot_sim_output(sim_output_melt = melt_sim3_cases, time_step = year, tick_label_evry = 1)
# output the plots p1 and p2 in a two column display
multi_ggplot(p5,p6 ,cols = 2)

```

```{r echo=FALSE}
# leave intentionally blank for formating purpose
```
+ ##### Figure caption: Plot of model simulation with no age structure but seasonal forcing of transmission parameter alone.

#### 4. Simulating the model with no age structure by imposing seasonal forcing on both the transmission of the bacteria and the risk of disease among colonized individuals.
```{r echo=TRUE}
sim4 = sample_sim(epsilon_a = 0.1, epsilon_b = 0.1, forcing_invasion = TRUE, nyears = 5, age_structured = FALSE)
# subset model output and choose variables to plot.
melt_sim4 =  melt_any_data.frame(sim4, "time", c("Susc", "Carrier", "Recov"))
melt_sim4_cases = melt_any_data.frame(sim4, "time", c("newI", "Ill"))
```

```{r echo=FALSE, fig.width=11, fig.height=4, fig.align='center'}

# Plot simulations
# Plot selected variables except cases
p7<-ggplot_sim_output(sim_output_melt = melt_sim4, time_step = year, tick_label_evry = 1)
# plot cases (iIncidence (NewI), and prevalence (Ill)) separetely with prevalence of cases
p8<-ggplot_sim_output(sim_output_melt = melt_sim4_cases, time_step = year, tick_label_evry = 1)
# output the plots p1 and p2 in a two column display
multi_ggplot(p7,p8 ,cols = 2)

```

```{r echo=FALSE}
# leave intentionally blank for formating purpose
```
+ ##### Figure caption: Plot of model simulation with no age structure but seasonal forcing of both transmission and invasion parameter.


### Data visualisation : Hyperendemic incidence data.

The data presented here are from health centers accross 4 sanitary districts of Burkina Faso and are included in this analysis because they had complete weekly notification data during at least one year. As we fitted our models on a yearly basis, a health center can contribute 1, 2, 3 or more  health center years in the analysis. 

```{r, message=FALSE, results="hide", cache=FALSE, fig.height=10}
#setwd(paste(getwd(),'R', sep = "/"))
#source('R/hyperendemic_data_visualisation.R', echo = TRUE)
source("R/plot_all_non_epi_data.R", echo = TRUE)
```

### Model calibration and parameter optimisation.

```{r }
    
```



